### 2022-08-19 README.Rmd
Added a bunch of functions to aid comparing scenarios. No EWN.
added functions to assist with comparing scenarios. How to reference TasHS without requiring TasHS still to be decided.
More functions to compare scenarios. No EWN
Added do_comparison and expanded comparisons. No EWN.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
suppressPackageStartupMessages({
  library(aMSE)
  library(TasHS)
  library(hutils)
  library(hplot)
  library(makehtml)
  library(knitr)
})
dbdir <- getDBdir()
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- paste0(dbdir,"A_CodeUse/aMSEUse/scenarios/")
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
confirmdir(rundir)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.

>>>>

* 2022-08-19 aMSE 0.0.15 Added do_comparison as a wrapper function for comparing scenarios.

* 2022-08-05 aMSE 0.0.14 Added more functions to assist with comparing scenarios.

* 2022-08-05 aMSE 0.0.12 Added more functions to assist with comparing scenarios. Still sorting out references to other packages.

* 2022-08-01 aMSE 0.0.11 Added a bunch of functions to assist with comparing scenarios. No EWN.

@@

```{r example, echo=TRUE, eval=FALSE }
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
suppressPackageStartupMessages({
  library(aMSE)
  library(TasHS)
  library(hutils)
  library(hplot)
  library(makehtml)
  library(knitr)
})
dbdir <- getDBdir()
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- paste0(dbdir,"A_CodeUse/aMSEUse/scenarios/")
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
confirmdir(rundir)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.
